---
title: "Regression"
author: "Brian Chang"
date: "Fall 2019"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = T)
```

# Lab Section

In this lab, we will go over regression. We will be using the caret package in R. https://topepo.github.io/caret/train-models-by-tag.html

# Perfomance Metrics 

## Residual 

Deviation of the observed value to the estimated value (sample mean)
$$residual=y_i - \hat{y_i}$$
where $\hat{y_i}$ is the estimated value

## Mean Squared Error (MSE)

$$MSE=\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y_i})^2$$

## Root Mean Squared Error (RMSE)
Same units as original data.

$$RMSE=\sqrt{MSE}$$

## L2 regularization : Ridge regression. Regularize by adding the sum of the coefficients, squared, to the function. 

$$Ridge Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p(w_j)^2$$

## L1 regularization : Lasso Regression. Regularize by adding the sum of the absolute value of the coefficients to the model. Coefficient estimates may be pushed to zero -- Lasso can perform variable selection

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$


\newpage

### The broad steps of Machine learning in R. 

1. Split the data into training and test. Set test aside. 

2. Fit a good model to the training data. 

3. See how your model did on the training data.

4. Test how your model performs on the test data. 

# Regression

```{r, include=FALSE}
library(caret)
library(MASS)
library(ggplot2)
library(dplyr)
library(ggfortify)
library(glmnet)
library(elasticnet)

#Mauna Loa CO2 concentrations
data(airquality)
```


1. Split data into training and test set (75% in train set, 25% in test set)

```{r split train and test}
set.seed(100)
trainIndex <- createDataPartition(airquality$Wind, p = .75, times = 1, list = FALSE)
train_regression <- airquality[trainIndex,]
test_regression <- airquality[-trainIndex,]
```


### Linear Regression

* Assumes a linear relationship. 
* Independent variables should not be correlated (no mulitcollinearity)
* The number of observations should be greater than the number of independent variables.


$$RSS=\sum(y_i - \hat{y_i})^2$$
We will predict the response of the Temperature based on Wind. 

This is the data we will fit a linear model to. 
```{r graph}
ggplot(data = train_regression) +
  geom_point(aes(x=Wind, y=Temp)) +
  theme_bw()
```

2. Create and fit a linear model to predict Temperature from Wind using the training set

```{r linear regression model}
#help(train)
set.seed(100)
linear_regression <- lm(Temp ~ Wind, data=train_regression)
```


3. Vizualize how your model performed on the train data by plotting the regression line on top of the train data points. 
```{r graph with line}
ggplot(data = train_regression, aes(x=Wind, y=Temp)) +
  geom_point() +
  theme_bw() +
  geom_line(data = fortify(linear_regression), aes(x = Wind, y = .fitted), color = 'red')
```


4. Explore how the model performs on the test data. For Linear Regression:

* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

4 a) See how the model performs on the test data
```{r predicting on test}
#help(predict)
linear_predict <- predict(linear_regression, newdata=test_regression)
print(linear_predict)
```

4 b) Look at the residuals. Are they close to zero?
```{r residuals}
#help(summary)
summary(linear_regression)
# the median residual is close to zero and the first quartile and third quartile are also not that far from zero
```


4 c) Plot predicted temperature vs observed temperature. A strong model should show a strong correlation
```{r predict vs observed}
# black points are observed values and red are the predicted
ggplot(test_regression, aes(x = Wind, y = Temp)) +
  geom_point() +
  geom_point(aes(y = linear_predict), color = 'red')
```

4 d) Visualize the predicted values in relation to the real data points. Look for homoscedasticity
```{r plot predicted vs. real}
# Extract coefficients from the model
coefficients(linear_regression)
# residual graph of predicted vs. observed
ggplot(data = test_regression, aes(x = Wind, y = Temp)) +
  geom_point(aes(x = Wind, y = Temp, color = 'Observed')) +
  geom_line(data = fortify(linear_regression), aes(x = Wind, y = .fitted)) +
  geom_segment(aes(xend = Wind, yend = linear_predict)) + 
  geom_point(aes(y = linear_predict, color = 'Predicted'))

```

4 e) Residuals should be normally distributed. Plot the density of the residuals
```{r density residual}
residuals_lin <- residuals(linear_regression)
# simple density plot 
plot(density(resid(linear_regression)), main = "Residual Density")

#ggplot(data=residvpredict) +
#  geom_density(aes(residual))
```


4 f) Independent variables and residuals should not be correlated
```{r}
cor.test(train_regression$Wind, resid(linear_regression))
```


### Linear Regression with Regularization

5. Create a linear model using L1 or L2 regularization to predict Temperature from Wind and Month variables. Plot your predicted values and the real Y values on the same plot. 

```{r regularization}

# L1 regularization and plot
l1_regularization <- train(Temp ~ Wind + Month, data=train_regression , method = "lasso")

l1_predict <- predict(l1_regularization, test_regression)
# L1 reguarlization plot predicted vs. observed (predicted in red)
ggplot(test_regression, aes(x = Wind, y = Temp)) +
  geom_point() +
  geom_point(aes(y = l1_predict), color = 'red')

# L2 regularization and plot
l2_regularization <- train(Temp ~ Wind + Month, data=train_regression , method = "ridge")
l2_predict <- predict(l2_regularization, test_regression)
# L2 reguarlization plot predicted vs. observed (predicted in red)
ggplot(test_regression, aes(x = Wind, y = Temp)) +
  geom_point() +
  geom_point(aes(y = l2_predict), color = 'red')
```


